Optimal design of experiment

### 2024-09-21 Sections/Literature_Review.tex
21.09

	The factorial methods can be used for parameter screening, giving main interaction effects of the considered factors with fewer runs. \citet{Ramandi2011} applied a full factorial design for screening the extraction parameters of fatty acids from \textit{Borago officinalis L.} flowers by SFE technique before optimisation using central composition design. Four factors: temperature, pressure, modifier volume and static extraction time were considered independent variables for full factorial design. All these factors were studied at two levels.

	\citet{Caldera2012} optimised extraction parameters of SFE to extract antioxidant compounds from rosemary. $2^3$ full factorial design was used to select important variables before optimisation of the selected factors by Box-Behnken design. Three factors, namely temperature, pressure and static extraction time, were studied in this experiment.

@@

	After an initial dataset has been collected and fitted to a mathematical model, the model undergoes further analysis. Additional experiments may be designed and conducted to differentiate between competing models that passed the preliminary tests. Once inadequate models are rejected, the remaining model may undergo another round of experiment design to enhance the precision of its parameters. This paper focuses on the final step of the validation procedure, known as model-based Design of Experiments (m-DoE), aimed at improving parameter precision. To the authors' knowledge, the m-DoE has not been applied to any case of supercritical extraction. The literature review below provides examples of this technique used in crystallization and pharmacology processes.

>>>>

	\citet{Ramandi2011} conducted a study to identify the variables with the greatest influence on the extraction yield of fatty acids from \textit{Borago officinalis L.} flowers using Supercritical Fluid Extraction (SFE). A Full Factorial Design was employed as a screening method, resulting in a design matrix of 32 runs ($2^5$) carried out randomly to minimize the impact of extraneous or nuisance variables. The low and high values for the factors were selected based on previous research. After determining the most significant variables, a Central Composite Design was applied to three factors—temperature, pressure, and modifier volume—to optimize the SFE conditions. This allowed for the modeling of the response surface by fitting a second-order polynomial.

	Similarly, \citet{Caldera2012} conducted a study to optimize SFE variables, specifically extraction pressure, extraction temperature, and static extraction time, for the maximum extraction of carnosol and carnosic acid from Venezuelan rosemary (\textit{Rosmarinus officinalis L.}) leaves. A $2^3$ Full Factorial Design was initially used to examine these three variables. Based on the statistically significant variables, a Box-Behnken design was employed to create a matrix of 15 experiments, which was used to further optimize the SFE process for maximum carnosol and carnosic acid extraction using Response Surface Methodology.

@@

	After an initial dataset has been collected and fitted to a mathematical model, the model undergoes further analysis. Additional experiments may be designed and conducted to differentiate between competing models that passed the preliminary tests. Once inadequate models are rejected, the remaining model may undergo another round of experiment design to enhance the precision of its parameters. This paper focuses on the final step of the validation procedure, known as model-based Design of Experiments (m-DoE), aimed at improving parameter precision. To the authors' knowledge, the m-DoE has not been applied to any case of supercritical extraction, so the further literature review provides examples of application in crystallization and pharmacology processes.
